---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)
```

```{css}
body {
  font-weight: Arial;
  background-color: #000000;
  color: #D4B690;
  padding: 10px
}

```

## Recommended Advertisements on Social Media Platforms  
In this report we are looking at the relevancy and pattern of the recommended advertisements for the user. Also attending to the platforms and length of time a user is online for.

```{r fig.width=12, fig.height=4}

#reading the csv file and assigning it to a data frame
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSWYoztEaAMyN953vtr_vpbcvnqGeBzSc58cwOJ3PVN4qLg6jiNBdm01CH7g5EnPGDDkgyi9FFsD1Ok/pub?output=csv")

#renaming the variable names in the logged_data data frame, and naming the new data frame latest_data
latest_data <- logged_data %>%
  rename(timestamp = 1,
         hours_online = 2,
         num_ads_hourly = 3,
         online_med = 4,
         ad_category = 5,
         satisfaction = 6)

#mean number of hours spent online, rounded to one decimal place
mean_hours_online <- latest_data$hours_online %>% 
  mean() %>% 
  round(1)

#maximum number of ads recommended in a hour
max_num_ads <- latest_data$num_ads_hourly %>% 
  max()

#dynamic comment using paste()
paste("It is reported that on average of", mean_hours_online, "hours were spent online daily, with up to", max_num_ads, "advertisements recommended per hour of online activity.")
```

This graph displays the online platforms that the user was on when recommended the surveyed advertisement.

```{r fig.width=12, fig.height=4}
#bar graph of the online mediums the advertisement was shown on
latest_data %>%
  ggplot() +
  geom_bar(aes(x = online_med), fill = "#FF7F50") +
  labs(title = "Online medium the advertisement was shown on",
       x = "Online Platforms",
       y = "Number of hours online",
       caption = "Source: STATS 220 survey S125")
```

Another graph here displays the distribution of the advertisement categories on various platforms.

```{r fig.width=12, fig.height=4}
#separates the multi-option variables in ad_category and assigning it to a new dataframe (sorted_ad_category)
sorted_ad_category <- latest_data %>%
  separate_rows(ad_category, sep = ';')

#bar graph of the number of appearances of each category of advertisements on various online platforms
sorted_ad_category %>%
  ggplot() +
  geom_bar(aes(y = online_med, fill = ad_category)) +
  labs(title = "Number of appearances of each category of advertisements on various online platforms",
       x = "Number of appearances",
       y = "Online platforms",
       fill = "Category of advertisements",
       caption = "Source: STATS 220 survey S125")
```

